---
title: "Regression Results"
format:
  html:
    embed-resources: true
toc: true
---

```{r}
library(dplyr)
library(here)

# load final analysis dataset
df <- readRDS(here("data", "output", "analysis_dataset.rds"))

# create state FE
df <- df |>
  mutate(
    state = substr(geoid, 1, 2),
    metro = case_when(
      stringr::str_detect(metro_description, stringr::regex("nonmetro", ignore_case = TRUE)) ~ 0,
      stringr::str_detect(metro_description, stringr::regex("metro", ignore_case = TRUE)) ~ 1,
      TRUE ~ NA_real_
    )
  )
```

## No Controls

```{r}
summary(lm(ami_energy_burden_all ~ data_center, data = df))
summary(lm(median_income ~ data_center, data = df))
summary(lm(gini ~ data_center, data = df))
summary(lm(log1p(current_dollar_gdp_thousands_of_current_dollars) ~ data_center, data = df))
```

## With State Fixed Effects

```{r}
summary(lm(ami_energy_burden_all ~ data_center + as.factor(state), data = df))
summary(lm(median_income ~ data_center + as.factor(state), data = df))
summary(lm(gini ~ data_center + as.factor(state), data = df))
summary(lm(log1p(current_dollar_gdp_thousands_of_current_dollars) ~ data_center + as.factor(state), data = df))
```

------------------------------------------------------------------------

log standardizing turns the beta coefficient into a percentage. that's why we're doing log1p() on the median income. (also big numbers make head hurt)

```{r with-log}
summary(lm(log1p(median_income) ~ data_center + as.factor(state), data = df))
```

we regress home values because we think that externalities would manifest through them. if there is noise pollution (or regular pollution) we would expect this to be captured by home valuation.

```{r home-value}
summary(lm(log1p(median_home_value) ~ data_center + as.factor(state), data = df))
summary(lm(log1p(median_rent) ~ data_center + as.factor(state), data = df)) # monthly rent btw
```

## metro control

With Metro Control

```{r}
summary(lm(ami_energy_burden_all ~ data_center + metro, data = df))
summary(lm(median_income ~ data_center + metro, data = df))
summary(lm(gini ~ data_center + metro, data = df))
summary(lm(log1p(current_dollar_gdp_thousands_of_current_dollars) ~ data_center + metro, data = df))
```

```{r}
summary(lm(ami_energy_burden_all ~ data_center + metro + as.factor(state), data = df))
summary(lm(median_income ~ data_center + metro + as.factor(state), data = df))
summary(lm(gini ~ data_center + metro + as.factor(state), data = df))
summary(lm(log1p(current_dollar_gdp_thousands_of_current_dollars) ~ data_center + metro + as.factor(state), data = df))
```

```{r}
summary(lm(log1p(median_income) ~ data_center + metro + as.factor(state), data = df))
```

```{r}
summary(lm(log1p(median_home_value) ~ data_center + metro + as.factor(state), data = df))
summary(lm(log1p(median_rent) ~ data_center + metro + as.factor(state), data = df))
```

## Income and GDP with Resident Age Control

```{r}
summary(lm(median_income ~ data_center + median_resident_age, data = df))
summary(lm(median_income ~ data_center + median_resident_age + as.factor(state), data = df))
summary(lm(log1p(current_dollar_gdp_thousands_of_current_dollars) ~ data_center + median_resident_age, data = df))
summary(lm(log1p(current_dollar_gdp_thousands_of_current_dollars) ~ data_center + median_resident_age + as.factor(state), data = df))
```

```{r age-wtf}
df_age_wtf <- df |> mutate(age_c = median_resident_age - mean(median_resident_age))

quad <- lm(median_income ~ data_center + age_c + I(age_c^2) + as.factor(state), data = df_age_wtf)

df_age_wtf |> 
  mutate(age_bin = cut(median_resident_age, breaks = 10)) |>
  group_by(age_bin) |>
  summarize(mean_income = mean(median_income))

summary(quad)$coefficients
```

```{r age-distracted}
summary(lm(median_income ~ data_center + median_resident_age + as.factor(state), data = df))
```

## With all controls

```{r control-with-metro}
summary(lm(median_income ~ data_center + median_resident_age + metro + as.factor(state), data = df))
```

## Energy Burden with Age Control

```{r}
summary(lm(ami_energy_burden_all ~ data_center + median_house_age, data = df))
summary(lm(ami_energy_burden_all ~ data_center + median_house_age + as.factor(state), data = df))
summary(lm(ami_energy_burden_all ~ data_center + median_house_age + metro + as.factor(state), data = df))
```

## Final Analysis

```{r final-analysis}
# Median Income (levels) 
summary(lm(median_income ~ data_center + median_resident_age + metro + as.factor(state), data = df))

# Median Income (log)

summary(lm(log1p(median_income) ~ data_center + metro + as.factor(state), data = df))

# GDP (log)

summary(lm(log1p(current_dollar_gdp_thousands_of_current_dollars) ~ data_center + median_resident_age + metro + as.factor(state), data = df))

# Energy Burden

summary(lm(ami_energy_burden_all ~ data_center + median_house_age + metro + as.factor(state), data = df))

# Inequality (Gini)

summary(lm(gini ~ data_center + metro + as.factor(state), data = df))

# Home Values (log)

summary(lm(log1p(median_home_value) ~ data_center + metro + as.factor(state), data = df))

# Rent (log)

summary(lm(log1p(median_rent) ~ data_center + metro + as.factor(state), data = df))


```
